Manuscript

### 2022-09-09 analysis/manuscript.Rmd
fix typo

## combine `max_C_plot` with `corr_vs_MR_effects_plot`

corr_vs_MR_comb <- plot_grid(plotlist = list(corr_vs_MR_effects_plot, max_C_plot), nrow=2, ncol = 1, byrow = T, labels="AUTO")

>>>>

## combine `summ_C_plot` with `corr_vs_MR_effects_plot`

corr_vs_MR_comb <- plot_grid(plotlist = list(corr_vs_MR_effects_plot, summ_C_plot), nrow=2, ncol = 1, byrow = T, labels="AUTO")
